From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-06-12 article/article.tex
Updated footnote to exlpain figure better.

The work by \cite{good2010performance} forms the basis of the motivation of the approach taken here.
In this study, the authors discovered that the modularity search space for many real-world networks contains a huge number of high value solutions.
Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E. coli} metabolic network reconstruction \cite{GuimeraNature2005}.
The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.

>>>>

The work by \cite{good2010performance} forms the basis of the motivation of the approach taken here.
In this study, the authors discovered that the modularity search space for many real-world networks contains a huge number of high value solutions.
Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E. coli} metabolic network reconstruction \cite{GuimeraNature2005}.
The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.
